Ethnicity sensitive author disambiguation using semi-supervised learning

### 2015-08-29 paper/paper.tex
save

\begin{table}
\caption{Average precision, recall and f-measure scores on test folds.}
\label{table:results}
\centering
\begin{tabular}{|l|c c c|c c c|}
  \hline
                       & \multicolumn{3}{|c|}{\textbf{B3}} & \multicolumn{3}{|c|}{\textbf{Pairwise}} \\
  \textbf{Description} & $P$ & $R$ & $F$ & $P$ & $R$ & $F$\\
  \hline
  \hline
Baseline & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
\hline
Blocking = SFI & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841 & 0.9927 & 0.9817 & 0.9871 \\
Blocking = NYSIIS & 0.9875 & 0.9826 & \textbf{0.9850} & 0.9936 & 0.9814 & \textbf{0.9875} \\
Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
\hline
No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
Name normalization & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
Classifier = GBRT & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
Classifier = Random Forests & 0.9909 & 0.9783 & \textbf{0.9846} & 0.9957 & 0.9752 & \textbf{0.9854} \\
Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666 & 0.9717 & 0.9569 & 0.9643 \\
\hline
Training pairs = Non-blocked, uniform & 0.9793 & 0.9630 & 0.9711 & 0.9756 & 0.9629 & 0.9692 \\
Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786 & 0.9850 & 0.9707 & 0.9778 \\
Training pairs = Blocked, balanced & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
Clustering = Average linkage & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671 & 0.9543 & 0.9626 & 0.9584 \\
Clustering = Complete linkage & 0.9862 & 0.9709 & 0.9785 & 0.9920 & 0.9688 & 0.9803 \\
\hline
No cut & 0.9024 & 0.9828 & 0.9409 & 0.8298 & 0.9776 & 0.8977 \\
Global cut & 0.9892 & 0.9737 & 0.9814 & 0.9940 & 0.9727 & 0.9832 \\
Block cut & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
Combined best settings  & 0.9910 & 0.9780 & \textbf{0.9845} & 0.9959 & 0.9750 & \textbf{0.9853} \\
  \hline
\end{tabular}
\end{table}

@@

\textit{Combined best settings.} When all best settings are combined (\ie,
Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
performance saturates at $0.9845$, which shows not to be better than the best
reported results ($0.9850$). Since the only difference between these two
solutions is the use of Random Forests instead of GBRT as classifiers, this
final result suggests that there appears to be no significant gain in using one rather
the other. Both tree-based methods show equally good performance. \glnote{Experiment was run incorrectly!! Results are being recomputed...}

>>>>

\begin{table}
\caption{Average precision, recall and f-measure scores on test folds.}
\label{table:results}
\centering
\begin{tabular}{|l|c c c|c c c|}
  \hline
                       & \multicolumn{3}{|c|}{\textbf{B3}} & \multicolumn{3}{|c|}{\textbf{Pairwise}} \\
  \textbf{Description} & $P$ & $R$ & $F$ & $P$ & $R$ & $F$\\
  \hline
  \hline
Baseline & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
\hline
Blocking = SFI & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841 & 0.9927 & 0.9817 & 0.9871 \\
Blocking = NYSIIS & 0.9875 & 0.9826 & \textbf{0.9850} & 0.9936 & 0.9814 & \textbf{0.9875} \\
Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
\hline
No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
Name normalization & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
Classifier = GBRT & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
Classifier = Random Forests & 0.9909 & 0.9783 & \textbf{0.9846} & 0.9957 & 0.9752 & \textbf{0.9854} \\
Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666 & 0.9717 & 0.9569 & 0.9643 \\
\hline
Training pairs = Non-blocked, uniform & 0.9793 & 0.9630 & 0.9711 & 0.9756 & 0.9629 & 0.9692 \\
Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786 & 0.9850 & 0.9707 & 0.9778 \\
Training pairs = Blocked, balanced & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
Clustering = Average linkage & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671 & 0.9543 & 0.9626 & 0.9584 \\
Clustering = Complete linkage & 0.9862 & 0.9709 & 0.9785 & 0.9920 & 0.9688 & 0.9803 \\
\hline
No cut & 0.9024 & 0.9828 & 0.9409 & 0.8298 & 0.9776 & 0.8977 \\
Global cut & 0.9892 & 0.9737 & 0.9814 & 0.9940 & 0.9727 & 0.9832 \\
Block cut & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
\hline
Combined best settings & 0.9897 & 0.9827 & \textbf{0.9862} & 0.9954 & 0.9805 & \textbf{0.9879} \\
  \hline
\end{tabular}
\end{table}

@@

\textit{Combined best settings.} When all best settings are combined (\ie,
Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
performance reaches  $0.9862$, combining the high recall of NYSIIS blocking
with the better precision of Random Forests.
